Manifold Destiny - or how to rig an election

### 2024-01-01 presentation.qmd
huxed

```{r, echo=F, caption="Example 1"}
## Tower 1
ex1m <- as.matrix(cbind(S,T,U,V))
towi <- as.data.frame(ex1m) %>% 
  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
  dplyr::select(5:8) %>%
  t() %>%
  data.frame() %>%
  data.table::setnames(paste0("County_",1:6))

towi[3:4,1] <- ""
towi[4,2] <- ""
lego_hux_nor_i <- hux(towi[,1:3]) 
lego_hux_nor_i 
```

```{r, echo=F, caption="Example 2"}
## Tower 2
ex2m <- as.matrix(cbind(S,T,Up,Vp))
towii <- as.data.frame(ex2m) %>% 
  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
  dplyr::select(5:8) %>%
  t() %>%
  data.frame() %>%
  data.table::setnames(paste0("County_",1:6))
towii[3:4,1] <- ""
towii[4,2] <- ""
lego_hux_nor_ii <- hux(towii[,1:3]) 
lego_hux_nor_ii 
```

>>>>

**Our numerical example**

:::: {.columns}
::: {.column width="50%"}
Case 1
:::
```{r, echo=F}
clr <- c("black","green","red","blue")
lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
  set_text_color(5, 1:2, clr[1]) %>%
  set_background_color(1, 1:3, clr[2]) %>% 
  set_background_color(2, 1:3, clr[3]) %>%
  set_background_color(3:5, 1:3, clr[4]) 
lego_hux_imp_i
```

::: {.column width="50%"}
Case 2
:::
```{r, echo=F}
lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%
  set_text_color(5, 1:2, clr[1]) %>%
  set_background_color(1, 1:3, clr[2]) %>% 
  set_background_color(2, 1:3, clr[3]) %>%
  set_background_color(3:5, 1:3, clr[4]) 
lego_hux_imp_ii
```
::::
